Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect

### 2021-06-23 paper_draft3.tex
more figures

\begin{figure}[h!]
\centering
  \caption{Plot of the growth function $g(u)$ compared to the identity function with growth parameters $\alpha=0.33$, $\beta=0.66$, and $\mu=0.5$.}
  \includegraphics{figures/fig1.png}
\end{figure}

@@

\item  for all $\lambda\in(0,1)$, for all $y\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-y)$ has at most one zero-crossing in $\mathbb R$.
\end{enumerate}
%\end{hyp}

@@

\begin{prop} \label{prop1}
%Let $\mathcal B$ denote the space of bounded, continuous, non-negative functions $\mathbb R \to \mathbb R$. $Q$ is a bounded nonlinear operator $\mathcal B \to \mathcal B$, and satisfies the following properties for all $u \in \mathcal B$:
The operator $Q$ satisfies the following properties for all bounded continuous functions $u : \mathbb R \to \mathbb R_{\geq 0}$:

\begin{enumerate}[(i.)]
\item \it{(Translation invariance)} $Q[T^t[u]]=T^t[Q[u]]$ for any translation operator $T^t[u](x)=u(x+t)$.
\item \it{(Symmetric)} If $u(x)=u(-x)$ then $Q[u](x)=Q[u](-x)$.
\item \it{(Limit-preserving)} If $u(x)\to\ell$ as $x\to\infty$, then $Q[u](x)\to g(\ell)$ as $x\to\infty$; likewise as $x\to-\infty$.
\end{enumerate}
\end{prop}

@@

The condition that $\sup_{x\in\mathbb R}w_2(x)\leq \b$ may be difficult to verify for some choices of dispersal kernel. Thus, we provide a sufficient condition for this assumption:
\begin{lem} \label{lemma}
Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. If $k(x)$ is unimodal and
$$ \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy \leq \b $$
then $\sup_{x\in\mathbb R}w_2(x) \leq \b$.
\end{lem}

\begin{proof}
For all $x\in\mathbb R$, we have
\begin{equation} \begin{aligned}
w_2(x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy  \\
&\leq\int_{-\infty}^{\infty} k(x-y) (\m + (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) )\, dy \\
&= \m + \int_{-\infty}^{\infty} k(x-y) (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) \, dy \\
&= \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy .
\end{aligned}
\end{equation}

Taking the maximum over all $x$, we may shift the function horizontally so that the bounds of integration are symmetric. Since $k(x)$ is unimodal, the integral is then maximized for $x=0$.
\begin{equation} \begin{aligned}
\sup_{x\in\mathbb R} w_2(x) &\leq \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy \right) \\
&= \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (x-y) \, dy \right) \\
&= \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy.
\end{aligned}
\end{equation}
\end{proof}

@@

The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data. We also assume the disperal kernel is compactly supported. First, we introduce a useful lemma for compactly supported kernels.

\begin{lem}\label{lemma2}
Suppose $k(x)$ is compactly supported on $[-\sigma,\sigma]$ for some $\sigma>0$, and let $u \in C(\mathbb R)$. If $u(x)=0$ for $x \in \Omega \subseteq \mathbb R$, then $(k*u)(x)=0$ if $d(x,\mathbb R\setminus\Omega):= \inf \{d(x,y) \mid y\in \mathbb R\setminus\Omega\}$.
\end{lem}

\begin{proof}
Let $x\in\Omega$ such that $d(x,\mathbb R\setminus\Omega) \geq \sigma$. Then $(x-\sigma,x+\sigma)$ is a subset of  $\Omega$ on which $u$ vanishes; thus $ (k*u)(x) = \int_{x-\sigma}^{x+\sigma}k(x-y)u(y)\,dy = 0.$
\end{proof}

\begin{thm} Let $u_0(x)$ be a non-negative continuous function with compact support such that the set $A=\{x\in\mathbb R:\a\leq u_0(x)\leq \b\}$ is connected. Suppose $k(x)$ has compact support, $\sup_{x\in\mathbb R}w_2(x)\leq \b$, and $c^* > 0$. For $A$ sufficiently large, the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
\begin{equation}
\lim_{n\to\infty}\inf_{|x|<n(c^*-\epsilon)}u_{n}(x)>0,
\end{equation}
and 
\begin{equation}
\lim_{n\to\infty}\sup_{|x|>n(c^*+\epsilon)}u_n(x)=0.
\end{equation}
for all $\epsilon>0$.
\end{thm}

@@

Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. Then, applying the growth function, we have
\begin{equation} g(u_1(x)) = \begin{cases}
0 & x<-r-x_\a \\
1 & -r-x_\a \leq x \leq -r-x_\b \\
m & -r-x_\b < x < r+x_\b \\
1 & r+x_\b \leq x \leq r+x_\a \\
0 & x > r+x_\a
\end{cases}
\end{equation}
Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$. Thus, by Lemma \ref{lemma2}, $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$. If we assume $r \geq x_\b+\sigma$, then $u_2(x)=Q[u_1](x)=Q[w_1](x-r)=w_2(x-r)$ for $x>0$.

@@

\begin{equation}
u_2(x) = Q[u_1](x) \begin{cases}
w_2(x-r) & x \geq 0 \\
w_2(-x+r) & x < 0 
\end{cases}
\end{equation}
Since $c^*\geq 0$, we have
\begin{equation}
g(u_2(x)) = \begin{cases}
0 & x < -r-2c^* \\
1 & -r-2c^* \leq x \leq r+2c^* \\
0 & x > r+2c^* 
\end{cases}
\end{equation}

@@

@@

The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3); the proof of (H4) is left in the appendix.

@@

\begin{equation}
w_1(x) =   \begin{cases} 
1 - \frac{1}{2}e^{x} & x \leq 0 \\
\frac{1}{2}e^{-x} & x > 0
\end{cases}
\end{equation}
and
%\begin{equation}\label{laplacew2}
%w_2(x) = \begin{cases}
%m - \frac{1}{2} e^{x - \alpha} + \frac{1-\m}{2} e^{x - \beta} & x < \beta \\
%1 - \frac{1}{2} e^{x-\alpha} - \frac{1-\m}{2} e^{-(x-\beta)} & \beta \leq x \leq \alpha \\
%\frac{1}{2} e^{-(x-\alpha)} - \frac{1-\m}{2} e^{-(x-\beta)} & x > \alpha
%\end{cases}
%\end{equation}
%\begin{equation} \label{w2laplace}
%w_2(x) = \begin{cases}
%m + C_1 e^x & x < x_\b \\
%1 - C_2 e^x - C_3 e^{-x} & x_\b \leq x \leq x_\a \\
%C_4 e^{-x} & x_\a < x 
%\end{cases} \end{equation}
%or equivalently

@@

where
\begin{equation}
x_\a = \begin{cases} -\ln(2\a) & \a\leq \frac{1}{2} \\ \ln(2-2\a) & \a > \frac{1}{2} \end{cases}, \quad
x_\b = \begin{cases} -\ln(2\b) & \b\leq \frac{1}{2} \\ \ln(2-2\b) & \b > \frac{1}{2} \end{cases} 
\end{equation}
This leads to an equation for the mean wave speed
\begin{equation}
c^* = \begin{cases}
\frac{1}{2}x_\a  + \frac{1}{2}\log \left( \frac{1 - (1-\m) e^{x_\b-x_\a}}{2\a} \right) & \a \leq w_2(x_\a) \\
\frac{1}{2}x_\a + \frac{1}{2} \log \left( 1-\a + \sqrt{(1-\a)^2 - (1-\mu) e^{x_\b-x_\a}} \right) & w_2(x_\a) < \a < w_2(x_\b) \\
\frac{1}{2}x_\a + \frac{1}{2} \log \left( \frac{2(\a-\m)}{(1-\m)e^{x_\a-x_\b}-1} \right) & \a \geq w_2(x_\b)
\end{cases} 
\end{equation}
and

\begin{equation} \begin{aligned}
C_1 &= \frac{1-\m}{2}e^{-x_\b} - \frac{1}{2}e^{-x_\a} \\
C_2 &= \frac{1}{2} e^{-x_\a} \\
C_3 &= \frac{1-\m}{2} e^{x_\b} \\
C_4 &= \frac{1}{2} e^{x_\a} - \frac{1-\m}{2} e^{x_\b}
\end{aligned} \end{equation}

%$x_\a=w_1^{-1}(\a)$, $x_\b=w_1^{-1}(\b)$, with
%$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
The constants $C_1,C_2,C_3$, and $C_4$ are continuous functions of the growth parameters $\alpha$, $\beta$, and $\mu$, with $C_2,C_3,C_4\geq0$. They can be expressed as piecewise expressions:
\newcommand{\Conecaseone}{\b(1-\m)-\a}
\newcommand{\Conecasetwo}{\frac{1-\m-4\a(1-\b)}{4(1-\b)}}
\newcommand{\Conecasethree}{- \frac{1-\b+\m(1-\a)}{4(1-\a)(1-\b)} }

\begin{equation}
C_1 = \begin{cases}
\Conecaseone & \a,\b \leq \frac{1}{2} \\
\Conecasetwo & \a\leq\frac{1}{2}<\b \\
\Conecasethree & \frac{1}{2}<\a,\b
\end{cases} \end{equation}

\newcommand{\Ctwocaseone}{\a}
\newcommand{\Ctwocasetwo}{\frac{1}{4(1-\a)}}

\begin{equation}
C_2 = \begin{cases}
\Ctwocaseone & \a \leq \frac{1}{2} \\
\Ctwocasetwo & \a > \frac{1}{2}
\end{cases} \end{equation}

\newcommand{\Cthreecaseone}{\frac{1-\m}{4\b}}
\newcommand{\Cthreecasetwo}{(1-\m)(1-\b)}

\begin{equation}
C_3 = \begin{cases}
\Cthreecaseone & \b \leq \frac{1}{2} \\
\Cthreecasetwo & \b > \frac{1}{2}
\end{cases} \end{equation}

\newcommand{\Cfourcaseone}{\frac{\b-\a(1-m)}{4\a\b}}
\newcommand{\Cfourcasetwo}{\frac{1-4\a(1-\m)(1-\b)}{4\a}}
\newcommand{\Cfourcasethree}{1-\a-(1-\m)(1-\b)}

\begin{equation}
C_4 = \begin{cases}
\Cfourcaseone & \a,\b \leq \frac{1}{2} \\
\Cfourcasetwo & \a\leq\frac{1}{2}<\b \\
\Cfourcasethree & \frac{1}{2}<\a,\b
\end{cases} \end{equation}

To find $c^*$, we can now condition on the values of $w_2(x_\a)$ and $w_2(x_\b)$.

\begin{enumerate}[{Case} 1.]
\item If $w_2(x_\alpha)=C_4e^{-x_\a}>\a$, then $2c^*$ lies on the third piece of \eqref{w2laplace}. Hence the mean wave speed is given by $c^*=\frac{1}{2}\ln(\frac{C_4}{\a})$.

\item If $w_2(x_\a)=C_4e^{-x_\a}\leq\a$ and $w_2(x_\b)=\m+C_1e^{x_\b}\geq\a$, then we solve the equation

$$ 1 - C_2e^{2c^*} - C_3e^{-2c^*} = \a $$

Multiplying through by $e^{2c^*}$ yields a quadratic in $e^{2c^*}$:

$$ C_2 e^{4c^*} + (a-1) e^{2c^*} + C_3 = 0 $$

Using the quadratic formula, we get two solutions to this equation. To determine which is correct, note that $w_2'(2c^*)$ must be negative. Since $C_2,C_3$ are negative, $w_2(x)$ is concave down on $[x_\b,x_\a]$, thus $w_2$ is increasing through the first solution and decreasing through the second. Clearly we must take the greater solution. Thus,
$$ c^* = \frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) $$

\item If  $w_2(x_\b)=\m+C_1e^{x_\b}<\a$, we have

$$ \m + C_1 e^{2c^*} = \a $$
implies
$$ c^* = \frac{1}{2} \ln \frac{\a-\m}{C_1} $$
\end{enumerate}

Our general formula is thus
\begin{equation}
c^* = \begin{cases}
\frac{1}{2} \ln \left( \frac{C_4}{\a} \right) & \a<C_4e^{-x_\a} \\
\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) & C_4e^{-x_\a}<\a<\m+C_1e^{x_\b} \\
\frac{1}{2} \ln \left( \frac{\a-\m}{C_1}\right) & \a>\m+C_1e^{x_\b}
\end{cases}
\end{equation}
We can write this formula more explicitly depending on the signs of $\a-\frac{1}{2}$ and $\b-\frac{1}{2}$ respectively.
%Let $c_1$ and $c_2$ denote the intermediate wave speeds measured at some threshold $0<h<m$. For this analysis we chose the threshold of $h=a$. Thus $c_1 = w_2^{-1}(a) - w_1^{-1}(a)=2c^*-\alpha$, and $c_2=2c^*+\alpha-c_1=2\alpha$. We can now define the relative fluctuation in wavespeed by
%
%$$ f = \frac{|c_1-c_2|}{c^*} = \frac{|2c^*-3\alpha|}{c^*} $$
%
%We can also consider
%
%$$ f^2 = \frac{(c_1-c_2)^2}{(c^*)^{2}} $$
%
%The derivative is
%
%$$ \frac{df^2}{da} = \frac{d}{da}(c_1-c_2)^2\frac{1}{(c^*)^2} $$
%
%$$ = 2(c_1-c_2)(\frac{dc_1}{da}-\frac{dc_2}{da})(c^*)^{-2} - 2(c_1-c_2)^2(c^*)^{-3} $$
%
%$$ = \frac{2(c_1-c_2)}{(c^*)^2}\left((\frac{dc_1}{da}-\frac{dc_2}{da}) - \frac{c_1-c_2}{c^*}\right) $$
%
%It follows that $f$ is differentiable with respect to all the parameters almost everywhere. We conjecture that
%
%$$ \frac{df}{da} \geq 0 , \quad \text{almost everywhere} $$
%
%We will first consider the case $a,b<\frac{1}{2}$, and $a<C_4e^{-\alpha}$. We then have $\alpha=-\ln(2a)$, $c^*=\frac{1}{2}\ln\frac{b-(1-m)a}{4a^2b}$ so that
%
%$$ f = \frac{|\ln\frac{b-(1-m)a}{4a^2b}+3\ln(2a)|}{\ln\frac{b-(1-m)a}{4a^2b}} $$
%$$ = \frac{|\ln(2a(b-(1-m)a))-\ln(b)|}{\ln(b-(1-m)a)-\ln(4a^2b)}  $$

\begin{enumerate}[{Case} 1.]

@@

@@

\begin{proof}[Proof of Proposition \ref{prop1}]

Let $u(x)$ be non-negative, continuous, and bounded.

\begin{enumerate}[(i.)]
\item For $t\in\mathbb R$, let $T^t$ denote the translation operator defined $T^t[u](x) = u(x+t)$. Then,
\begin{equation} \begin{aligned}
Q[T^t[u]](x) &= 
\int_{-\infty}^{\infty} k(x-y) g(T^t[u](y)) \, dy \\
&= \int_{-\infty}^{\infty} k(x-y) g(u(y+t)) \, dy
\end{aligned} \end{equation}
Let $z=y+t$.
\begin{equation} \begin{aligned}
Q[T^t[u]](x)
&= \int_{-\infty}^{\infty} k(x-z+t) g(u(z)) \, dz \\
&= Q[u](x+t) \\
&= T^t[Q[u]](x)
\end{aligned} \end{equation}

\item 
Suppose $\lim_{x\to\infty}u(x)=\ell$.

\end{proof}

\begin{lem}
The Laplace kernel \eqref{laplacekernel} satisfies hypothesis (H4).
\end{lem}

\begin{proof}
let $f=f_{m,y}$ be the scalar function of $x$ with two parameters $y\in\mathbb R$ and $\mu\in(0,1)$ defined by
$$ f(x)= f_{m,y}(x) = \frac{1}{2} e^{-|x|} - \frac{\mu}{2}e^{-|x-y|} $$

>>>>

\begin{figure}[h!]
\centering
  \caption{Plot of the growth function $g(u)$ compared to the identity function with growth parameters $\alpha=0.33$, $\beta=0.66$, and $\mu=0.5$.}
  \includegraphics[width=.8\linewidth]{figures/fig1.png}
\end{figure}

@@

\item  for all $\lambda\in(0,1)$, for all $a\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-a)$ has at most one zero-crossing in $\mathbb R$.
\end{enumerate}
%\end{hyp}

@@

%\begin{prop} \label{prop1}
%%Let $\mathcal B$ denote the space of bounded, continuous, non-negative functions $\mathbb R \to \mathbb R$. $Q$ is a bounded nonlinear operator $\mathcal B \to \mathcal B$, and satisfies the following properties for all $u \in \mathcal B$:
%The operator $Q$ satisfies the following properties for all bounded continuous functions $u : \mathbb R \to \mathbb R_{\geq 0}$:
%
%\begin{enumerate}[(i.)]
%\item \it{(Translation invariance)} $Q[T^t[u]]=T^t[Q[u]]$ for any translation operator $T^t[u](x)=u(x+t)$.
%\item \it{(Symmetric)} If $u(x)=u(-x)$ then $Q[u](x)=Q[u](-x)$.
%\item \it{(Limit-preserving)} If $u(x)\to\ell$ as $x\to\infty$, then $Q[u](x)\to g(\ell)$ as $x\to\infty$; likewise as $x\to-\infty$.
%\end{enumerate}
%\end{prop}

@@

%The condition that $\sup_{x\in\mathbb R}w_2(x)\leq \b$ may be difficult to verify for some choices of dispersal kernel. Thus, we provide a sufficient condition for this assumption:
%\begin{lem} \label{lemma}
%Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. If $k(x)$ is unimodal and
%$$ \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy \leq \b $$
%then $\sup_{x\in\mathbb R}w_2(x) \leq \b$.
%\end{lem}
%
%\begin{proof}
%For all $x\in\mathbb R$, we have
%\begin{equation} \begin{aligned}
%w_2(x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy  \\
%&\leq\int_{-\infty}^{\infty} k(x-y) (\m + (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) )\, dy \\
%&= \m + \int_{-\infty}^{\infty} k(x-y) (\m-1) \mathbf 1_{[x_\b,x_\a]}(y) \, dy \\
%&= \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy .
%\end{aligned}
%\end{equation}
%
%Taking the maximum over all $x$, we may shift the function horizontally so that the bounds of integration are symmetric. Since $k(x)$ is unimodal, the integral is then maximized for $x=0$.
%\begin{equation} \begin{aligned}
%\sup_{x\in\mathbb R} w_2(x) &\leq \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{x_\b}^{x_\a} k (x-y) \, dy \right) \\
%&= \sup_{x\in\mathbb R} \left( \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (x-y) \, dy \right) \\
%&= \m +  (1-\mu)\int_{-(x_\a-x_\b)/2}^{(x_\a-x_\b)/2} k (y) \, dy.
%\end{aligned}
%\end{equation}
%\end{proof}

@@

The next theorem concerns the spreading behavior of solutions to the IDE \eqref{q} with compactly supported initial data. We also assume the disperal kernel is compactly supported.% First, we introduce a useful lemma for compactly supported kernels.

%\begin{lem}\label{lemma2}
%Suppose $k(x)$ is compactly supported on $[-\sigma,\sigma]$ for some $\sigma>0$, and let $u \in C(\mathbb R)$. If $u(x)=0$ for $x \in \Omega \subseteq \mathbb R$, then $(k*u)(x)=0$ if $d(x,\mathbb R\setminus\Omega):= \inf \{d(x,y) \mid y\in \mathbb R\setminus\Omega\}$.
%\end{lem}
%
%\begin{proof}
%Let $x\in\Omega$ such that $d(x,\mathbb R\setminus\Omega) \geq \sigma$. Then $(x-\sigma,x+\sigma)$ is a subset of  $\Omega$ on which $u$ vanishes; thus $ (k*u)(x) = \int_{x-\sigma}^{x+\sigma}k(x-y)u(y)\,dy = 0.$
%\end{proof}

\begin{thm} Suppose $k(x)$ has compact support and $\sup_{x\in\mathbb R}w_2(x)\leq \b$. Let $u_0(x)$ be a non-negative continuous function, and let $A=\{x\in\mathbb R:\a\leq u_0(x)\leq \b\}$. If $A$ is connected with sufficiently large radius and $c^* \geq 0$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by $u_{n+1}=Q[u_n]$, $n\geq 0$ spreads with speed $c^*$, i.e.
\begin{equation}
\lim_{n\to\infty}\inf_{|x|<n(c^*-\epsilon)}u_{n}(x)>0,
\end{equation}
and 
\begin{equation}
\lim_{n\to\infty}\sup_{|x|>n(c^*+\epsilon)}u_n(x)=0.
\end{equation}
for all $\epsilon>0$.
\end{thm}

@@

Let $x_\a$ and $x_\b$ be as defined in Lemma \ref{lemma1}. Then, applying the growth function, we have
\begin{equation} g(u_1(x)) = \begin{cases}
0 & x<-r-x_\a \\
1 & -r-x_\a \leq x \leq -r-x_\b \\
m & -r-x_\b < x < r+x_\b \\
1 & r+x_\b \leq x \leq r+x_\a \\
0 & x > r+x_\a
\end{cases}
\end{equation}
Note that $g(u_1(x))=g(w_1(x))$ for all $x >-r-x_\b$. Thus $Q[u_1](x)=(k*(g\circ u_1))(x)=(k*(g\circ w_1))(x)=Q[w_1](x)$ for all $x>-r-x_\b+\sigma$. If we assume $r \geq x_\b+\sigma$, then $u_2(x)=Q[u_1](x)=Q[w_1](x-r)=w_2(x-r)$ for $x>0$.

@@

\begin{equation}
u_2(x) = Q[u_1](x) = \begin{cases}
w_2(x-r) & x \geq 0 \\
w_2(-x+r) & x < 0 
\end{cases}
\end{equation}
Since $c^*\geq 0$, we have
\begin{equation}
g(u_2(x)) = \begin{cases}
0 & x < -r-2c^* \\
1 & -r-2c^* \leq x \leq r+2c^* \\
0 & x > r+2c^* 
\end{cases}
\end{equation}

@@

\begin{figure}[h!] 
\centering
  \caption{Spreading behavior for a uniform dispersal kernel with $\alpha=0.3$, $\mu=0.6$, and $\beta=0.7$. The time steps corresponding to $w_1(x)$ are colored in blue, while time steps corresponding to $w_2(x)$ are colored in red.}
\label{fig5}
  \includegraphics[width=.8\linewidth]{figures/fig5.png}
\end{figure}

@@

The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3); the proof of (H4) is left in the appendix \ref{laplaceproof}.

@@

\begin{equation} \label{w1laplace}
w_1(x) =   \begin{cases} 
1 - \frac{1}{2}e^{x} & x \leq 0 \\
\frac{1}{2}e^{-x} & x > 0
\end{cases}
\end{equation}
and
%\begin{equation}\label{laplacew2}
%w_2(x) = \begin{cases}
%m - \frac{1}{2} e^{x - \alpha} + \frac{1-\m}{2} e^{x - \beta} & x < \beta \\
%1 - \frac{1}{2} e^{x-\alpha} - \frac{1-\m}{2} e^{-(x-\beta)} & \beta \leq x \leq \alpha \\
%\frac{1}{2} e^{-(x-\alpha)} - \frac{1-\m}{2} e^{-(x-\beta)} & x > \alpha
%\end{cases}
%\end{equation}
%\begin{equation} \label{w2laplace}
%w_2(x) = \begin{cases}
%m + C_1 e^x & x < x_\b \\
%1 - C_2 e^x - C_3 e^{-x} & x_\b \leq x \leq x_\a \\
%C_4 e^{-x} & x_\a < x 
%\end{cases} \end{equation}
%or equivalently

@@

where
\begin{equation}
x_\a = \begin{cases} -\ln(2\a) & \a\leq \frac{1}{2} \\ \ln(2-2\a) & \a > \frac{1}{2} \end{cases}, \quad
x_\b = \begin{cases} -\ln(2\b) & \b\leq \frac{1}{2} \\ \ln(2-2\b) & \b > \frac{1}{2} \end{cases} 
\end{equation}
A necessary condition for formulas \eqref{w1laplace} and \eqref{w2laplace} to generate a periodic traveling wave solution are given in Lemma \ref{laplacebound}. This leads to an equation for the mean wave speed
\begin{equation}
c^* = \begin{cases}
\frac{1}{2}x_\a  + \frac{1}{2}\log \left( \frac{1 - (1-\m) e^{x_\b-x_\a}}{2\a} \right) & \a \leq w_2(x_\a) \\
\frac{1}{2}x_\a + \frac{1}{2} \log \left( 1-\a + \sqrt{(1-\a)^2 - (1-\mu) e^{x_\b-x_\a}} \right) & w_2(x_\a) < \a < w_2(x_\b) \\
\frac{1}{2}x_\a + \frac{1}{2} \log \left( \frac{2(\a-\m)}{(1-\m)e^{x_\a-x_\b}-1} \right) & \a \geq w_2(x_\b)
\end{cases} 
\end{equation}
%and
%\begin{equation} \begin{aligned}
%C_1 &= \frac{1-\m}{2}e^{-x_\b} - \frac{1}{2}e^{-x_\a} \\
%C_2 &= \frac{1}{2} e^{-x_\a} \\
%C_3 &= \frac{1-\m}{2} e^{x_\b} \\
%C_4 &= \frac{1}{2} e^{x_\a} - \frac{1-\m}{2} e^{x_\b}
%\end{aligned} \end{equation}
%%$x_\a=w_1^{-1}(\a)$, $x_\b=w_1^{-1}(\b)$, with
%%$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
%The constants $C_1,C_2,C_3$, and $C_4$ are continuous functions of the growth parameters $\alpha$, $\beta$, and $\mu$, with $C_2,C_3,C_4\geq0$. They can be expressed as piecewise expressions:
\newcommand{\Conecaseone}{\b(1-\m)-\a}
\newcommand{\Conecasetwo}{\frac{1-\m-4\a(1-\b)}{4(1-\b)}}
\newcommand{\Conecasethree}{- \frac{1-\b+\m(1-\a)}{4(1-\a)(1-\b)} }
%\Conecaseone & \a,\b \leq \frac{1}{2} \\
%\Conecasetwo & \a\leq\frac{1}{2}<\b \\
%\Conecasethree & \frac{1}{2}<\a,\b
\newcommand{\Ctwocaseone}{\a}
\newcommand{\Ctwocasetwo}{\frac{1}{4(1-\a)}}
%\Ctwocaseone & \a \leq \frac{1}{2} \\
\newcommand{\Cthreecaseone}{\frac{1-\m}{4\b}}
\newcommand{\Cthreecasetwo}{(1-\m)(1-\b)}
%\Cthreecaseone & \b \leq \frac{1}{2} \\
\newcommand{\Cfourcaseone}{\frac{\b-\a(1-m)}{4\a\b}}
\newcommand{\Cfourcasetwo}{\frac{1-4\a(1-\m)(1-\b)}{4\a}}
\newcommand{\Cfourcasethree}{1-\a-(1-\m)(1-\b)}
%\Cfourcaseone & \a,\b \leq \frac{1}{2} \\
%\Cfourcasetwo & \a\leq\frac{1}{2}<\b \\
%\Cfourcasethree & \frac{1}{2}<\a,\b
%To find $c^*$, we can now condition on the values of $w_2(x_\a)$ and $w_2(x_\b)$.
%\item If $w_2(x_\alpha)=C_4e^{-x_\a}>\a$, then $2c^*$ lies on the third piece of \eqref{w2laplace}. Hence the mean wave speed is given by $c^*=\frac{1}{2}\ln(\frac{C_4}{\a})$.
%\item If $w_2(x_\a)=C_4e^{-x_\a}\leq\a$ and $w_2(x_\b)=\m+C_1e^{x_\b}\geq\a$, then we solve the equation
%$$ 1 - C_2e^{2c^*} - C_3e^{-2c^*} = \a $$
%Multiplying through by $e^{2c^*}$ yields a quadratic in $e^{2c^*}$:
%$$ C_2 e^{4c^*} + (a-1) e^{2c^*} + C_3 = 0 $$
%Using the quadratic formula, we get two solutions to this equation. To determine which is correct, note that $w_2'(2c^*)$ must be negative. Since $C_2,C_3$ are negative, $w_2(x)$ is concave down on $[x_\b,x_\a]$, thus $w_2$ is increasing through the first solution and decreasing through the second. Clearly we must take the greater solution. Thus,
%$$ c^* = \frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) $$
%\item If  $w_2(x_\b)=\m+C_1e^{x_\b}<\a$, we have
%$$ \m + C_1 e^{2c^*} = \a $$
%$$ c^* = \frac{1}{2} \ln \frac{\a-\m}{C_1} $$
%\frac{1}{2} \ln \left( \frac{C_4}{\a} \right) & \a<C_4e^{-x_\a} \\
%\frac{1}{2} \ln \left( \frac{1-\a + \sqrt{(1-\a)^2 - 4C_2C_3}}{2C_2} \right) & C_4e^{-x_\a}<\a<\m+C_1e^{x_\b} \\
%\frac{1}{2} \ln \left( \frac{\a-\m}{C_1}\right) & \a>\m+C_1e^{x_\b}
%We can write this formula more explicitly depending on the signs of $\a-\frac{1}{2}$ and $\b-\frac{1}{2}$ respectively.
%Let $c_1$ and $c_2$ denote the intermediate wave speeds measured at some threshold $0<h<m$. For this analysis we chose the threshold of $h=a$. Thus $c_1 = w_2^{-1}(a) - w_1^{-1}(a)=2c^*-\alpha$, and $c_2=2c^*+\alpha-c_1=2\alpha$. We can now define the relative fluctuation in wavespeed by
%$$ f = \frac{|c_1-c_2|}{c^*} = \frac{|2c^*-3\alpha|}{c^*} $$
%We can also consider
%$$ f^2 = \frac{(c_1-c_2)^2}{(c^*)^{2}} $$
%The derivative is
%$$ \frac{df^2}{da} = \frac{d}{da}(c_1-c_2)^2\frac{1}{(c^*)^2} $$
%$$ = 2(c_1-c_2)(\frac{dc_1}{da}-\frac{dc_2}{da})(c^*)^{-2} - 2(c_1-c_2)^2(c^*)^{-3} $$
%$$ = \frac{2(c_1-c_2)}{(c^*)^2}\left((\frac{dc_1}{da}-\frac{dc_2}{da}) - \frac{c_1-c_2}{c^*}\right) $$
%It follows that $f$ is differentiable with respect to all the parameters almost everywhere. We conjecture that
%$$ \frac{df}{da} \geq 0 , \quad \text{almost everywhere} $$
%We will first consider the case $a,b<\frac{1}{2}$, and $a<C_4e^{-\alpha}$. We then have $\alpha=-\ln(2a)$, $c^*=\frac{1}{2}\ln\frac{b-(1-m)a}{4a^2b}$ so that
%$$ f = \frac{|\ln\frac{b-(1-m)a}{4a^2b}+3\ln(2a)|}{\ln\frac{b-(1-m)a}{4a^2b}} $$
%$$ = \frac{|\ln(2a(b-(1-m)a))-\ln(b)|}{\ln(b-(1-m)a)-\ln(4a^2b)}  $$

Our formula can be written more explicitly based on the values of $\a$ and $\b$:
\begin{enumerate}[{Case} 1.]

@@

\begin{figure}[h!] 
\centering
  \caption{The shaded region $R$ indicates all pairs $(\a,\b)$ such that the condition in Theorem 2.1 holds for $\m=0.6$, and the line $\b=2\a$ is drawn in red. The region $R_1$ contains all pairs $(\a,\b)$ such that the traveling wave has constant speed, and $R_2$ contains all pairs such that the traveling wave has oscillating speed.}
\label{fig4}
  \includegraphics[width=.5\linewidth]{figures/fig4.png}
\end{figure}

@@

%\begin{proof}[Proof of Proposition \ref{prop1}]
%
%Let $u(x)$ be non-negative, continuous, and bounded.
%
%\begin{enumerate}[(i.)]
%\item For $t\in\mathbb R$, let $T^t$ denote the translation operator defined $T^t[u](x) = u(x+t)$. Then,
%\begin{equation} \begin{aligned}
%Q[T^t[u]](x) &= 
%\int_{-\infty}^{\infty} k(x-y) g(T^t[u](y)) \, dy \\
%&= \int_{-\infty}^{\infty} k(x-y) g(u(y+t)) \, dy
%\end{aligned} \end{equation}
%Let $z=y+t$.
%\begin{equation} \begin{aligned}
%Q[T^t[u]](x)
%&= \int_{-\infty}^{\infty} k(x-z+t) g(u(z)) \, dz \\
%&= Q[u](x+t) \\
%&= T^t[Q[u]](x)
%\end{aligned} \end{equation}
%
%\item 
%Suppose $\lim_{x\to\infty}u(x)=\ell$. 
%
%\end{enumerate}
%
%\end{proof}

\begin{lem} \label{laplaceproof}
The Laplace kernel \eqref{laplacekernel} satisfies hypothesis (H4).
\end{lem}
